Spin canonical divisors of log stacky curves

### 2015-06-30 stacky_write_up/spin_cring.tex
theta-characteristics -> theta characteristic

The pairs $(\sx, \Delta)$ are called \textbf{log stacky curves}
and the study of their canonical rings is the main focus of
the work by Voight and Zureick-Brown \cite{vzb:stacky}.
For this paper, we consider \textbf{log spin curves} which are
triples $(\sx, \Delta, \halfcan)$ where $\Delta$ is a log divisor
and a divisor $\halfcan$ which satisfies the property that
$2\halfcan \sim K_\sx + \Delta$. Such a divisor $\halfcan$
is called a \textbf{log spin canonical divisor} on $(\sx, \Delta)$. We also use $\halfcan_X$ to refer to the spin canonical
divisor (also known as the half-canonical divisor, semi-canonical
divisor, or theta-characteristics) associated with the coarse space $X$ of $\sx$, i.e.
$\halfcan_X$ is a divisor such that $2\halfcan \sim K_X$.
Furthermore, we use the following analogous notations:

>>>>

The pairs $(\sx, \Delta)$ are called \textbf{log stacky curves}
and the study of their canonical rings is the main focus of
the work by Voight and Zureick-Brown \cite{vzb:stacky}.
For this paper, we consider \textbf{log spin curves} which are
triples $(\sx, \Delta, \halfcan)$ where $\Delta$ is a log divisor
and a divisor $\halfcan$ which satisfies the property that
$2\halfcan \sim K_\sx + \Delta$. Such a divisor $\halfcan$
is called a \textbf{log spin canonical divisor} on $(\sx, \Delta)$. 
We also use $\halfcan_X$ to refer to the spin canonical divisor
(also known as the half-canonical divisor, semi-canonical divisor, 
or a theta characteristic in other literature) associated with the
coarse space $X$ of $  \sx$, i.e. $\halfcan_X$ is a divisor such
that $2\halfcan \sim K_X$. Furthermore, we use the following
analogous notations:
